Measuring Software Ticket Quality using Quantitative Data Analysis

### 2018-04-21 paper/paper.tex
Fix issues inside paper

@@

Software tickets can have duplicates, usually meaning that the most important fields, such 
as summary or description, describe the same feature request or bug report. Even though 
one might believe that they cannot bring any value to a software project, the work of 
Bettenburg et. al \cite{bettenburg2008duplicate} shows the contrary.
The authors collected large amounts of data from the Eclipse open source project and ran
various kind of textual and statistical analysis on the data to find answers.
After the results were computed, they concluded that usually bug duplicates contain 
information that is not present in the master report (i.e. the original report that was 
filed). Moreover, developers also specified that they have often found value in these 
duplicate bug reports and that they can even aid automated triaging techniques.

>>>>

In this section we will present what are the state-of-the art studies in the issue/ticket quality 
field. More specifically, we will look at research papers that investigated what makes for a valuable ticket, 
how can one extract structured/unstructured data from tickets (e.g. stack traces), ticket duplication and its 
positive and negative outcomes, quality of modern issue tracking systems as well as automating the process 
of summarizing tickets or the optimal assignee.

@@

Software tickets can have duplicates, usually meaning that the most important fields, such 
as summary or description, describe the same feature request or bug report. Even though 
one might believe that they cannot bring any value to a software project, the work of 
Bettenburg et. al \cite{bettenburg2008duplicate} shows the contrary.
The authors collected large amounts of data from the Eclipse open source project and ran
various kind of textual and statistical analysis on the data to find answers.
After the results were computed, they concluded that usually bug duplicates contain 
information that is not present in the master report (i.e. the original report that was 
filed). Also, developers also specified that they have often found value in these 
duplicate bug reports and that they can even aid automated triaging techniques.

%TODO: ADD HERE PROPER PAPER
However, the study conducted by Cavalcanti et. al \cite{cavalcanti2013bug} shows completely 
different results. The authors investigated around 280,000 tickets from multiple open and 
closed source repositories and found that having bug duplicates
97,000 tickets from the Mozilla repository in order to infer the quality of merging duplicate
bug reports. Their results are statistically significant and they show that merging bug report 
duplicates improved the overall quality of the project (i.e. )
